---
title: "Clarification on terminology"
output: html_document
---

# Terms 

A number of terms crop up throughout this site that may lead to confusion if not addressed properly.

## Code and functions

Before diving into terms, we note how we will use fonts in the site. 
Firstly, any command or object that could be considered code will be shown as 
`code`. For example, typing "sum(a + b)" in the console will be shown as `sum(a + b)`. Likewise, 
functions will always be denoted in this code format, but with the addition of 
open and closed parentheses. For example, the function "foo" will be denoted
as `foo()`. 

## Variables and objects

In R, a *variable* refers to the name of a stored value. For example:

```{r eval = FALSE}
my.vector <- c(9, 10, 11)
```
Here, `my.vector` holds the vector `c(9, 10, 11)` and will refer to it when we do operations with `my.vector`. Sometimes programmers also refer to `my.vector` as an *object* since it is a type of object within the syntax of R.

In the EPA API, a *variable* refers to a desired data filtering characteristic in a URL request. For example, in the URL,

> https://aqs.epa.gov/data/api/dailyData/byState?&email=youremail@domain.com&key=yourapikey&state=37

`state` is considered a variable for the URL since data will be queried according to a particular state.

To avoid confusion, we will always refer to variables referring to the API as an *API variable*. When dealing with R variables, we will call them an *object* or specifically call them by their R data type like an *R list*. For example, through out this tutorial, we will often times reference `services` or `variables`. These are both R objects (i.e. a list or dataframe) loaded in with `epair`, and they are each an R variable containing information about the EPA API.

## Parameter codes

In the wider world of mathematics, a *parameter* can mean a value passed into a function. 
For example,

```{r eval = FALSE}
foo(a, b)
```
Here, `a` and  `b` are considered parameters of the function `foo()` since they are passed into 
the function as inputs. 

In the EPA API, there are *parameter codes*. These refer to the 
particular way an API variable should be used. For instance, taking a look at the URL 
we showed above, 

> https://aqs.epa.gov/data/api/dailyData/byState?&email=youremail@domain.com&key=yourapikey&state=37

we see that `state = 37`. Here, `37` is the *parameter code* for the `state` API variable, and 
this code must be constructed in a particular way to match its API variable. Another example, 
is with the following URL, 

> https://aqs.epa.gov/data/api/dailyData/byState?&email=youremail@domain.com&key=yourapikey&state=37&bdate=20200101&edate=20200102&param=44201

We note that `bdate` is an API variable referring to the beginning date desired for the data. Its *parameter code* is `20200101`. Likewise, the `param` API variable has a *parameter code* of `44201`. 

In this site, we will refer to values passed into a function as *arguments* and *parameter codes* will refer to the encoding value needed in an API variable. 




