---
title: "Summary"
output: rmarkdown::html_vignette
description: >
  Wrap up
vignette: >
  %\VignetteIndexEntry{Summary}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Now you know how to make calls! The general template for making a call (after making sure authentication is set up) is as follows.

1. Determine an endpoint for your service (possibly with the `services` object).

```{r eval = FALSE}
endpoint <- 'APIEndpoint'
```

2. Make the call with `perform.call()`.

```{r eval = FALSE}
result <- perform.call(endpoint)
```

3. If the call requires a single variable, declare the variable with the API variable name and pass it in as a second argument 
in `perform.call()`.

```{r eval = FALSE}
variable <- "value"
result <- perform.call(endpoint, variable)
```

Or, specify the name of the API variable in the third argument.

```{r eval = FALSE}
variable.code <- "value"
result <- perform.call(endpoint, variable.code, name = "API variable name")
```

4. If the call requires multiple variables, make a list and pass it in as a second argument
in `perform.call()`.

```{r eval = FALSE}
variables <- list(variable.one = "value.one",
                  variable.two = "value.two",
                  variable.three = "value.three")
result <- perform.call(endpoint, variables)
```

Or, specify the names of parameter codes in the second argument.

```{r eval = FALSE}
variables <- list("value.one", "value.two", "value.three")
result <- perform.call(endpoint, 
                       variables,
                       name = list("variable.one", "variable.two", "variable.three"))
```
